### 2023-08-08 chapters/paper_modelagnostic.tex
Fix compilation issue and revise captions

\begin{figure*}[tbp]
    \includegraphics[width=\textwidth]{graphics/paper_modelagnostic/pvalues_comb_no_drop_correct_font.pdf}
    \caption{\emph{First plot}: $p$-values of the typicality test on the two test sets. We can see that under $\mathcal{H}_0$, they should be uniformly distributed. \emph{Second plot}: $p$-values of the score statistic. \emph{Third plot}: values obtained by the Fisher's method. In red, we plot the density function of a $\chi^2$-distribution with 4 degrees. This shows that the statistics are independent. \emph{Fourth plot}: $p$-values obtained of the combination. These plots refer to a PixelCNN++ trained on FashionMNIST without dropout.}
    \label{fig_modelagnostic:comb_p_values}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%% FIGURE
\begin{figure}[tb]
    \centering
    \includegraphics[scale=0.48]{graphics/paper_modelagnostic/fashion_hvae_type1_correct_font.pdf}
    \caption{Type I (probability of an inlier to be classified as outlier) and Type II (probability of an outlier to be considered as inlier) errors versus the significance level $\alpha$ on the combination values. By using Benjamini-Hochberg correction, we get that the Type I error stays below identity line.}
    \label{fig_modelagnostic:type1}
\end{figure}

>>>>

\begin{figure*}[tbp]
    \includegraphics[width=\textwidth]{graphics/paper_modelagnostic/pvalues_comb_no_drop_correct_font.pdf}
    \caption[Distribution of the p-values of the typicality test, score statistic, Fisher's method and a combination of all.]{\emph{First plot}: $p$-values of the typicality test on the two test sets. We can see that under $\mathcal{H}_0$, they should be uniformly distributed. \emph{Second plot}: $p$-values of the score statistic. \emph{Third plot}: values obtained by the Fisher's method. In red, we plot the density function of a $\chi^2$-distribution with 4 degrees. This shows that the statistics are independent. \emph{Fourth plot}: $p$-values obtained of the combination. These plots refer to a PixelCNN++ trained on FashionMNIST without dropout.}
    \label{fig_modelagnostic:comb_p_values}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%% FIGURE
\begin{figure}[tb]
    \centering
    \includegraphics[scale=0.48]{graphics/paper_modelagnostic/fashion_hvae_type1_correct_font.pdf}
    \caption[Type I and Type II errors versus the significance level $\alpha$ on the combination values]{Type I (probability of an inlier to be classified as outlier) and Type II (probability of an outlier to be considered as inlier) errors versus the significance level $\alpha$ on the combination values. By using Benjamini-Hochberg correction, we get that the Type I error stays below identity line.}
    \label{fig_modelagnostic:type1}
\end{figure}
